class: center, middle, inverse

# `r icon::fa("chart-line", size = 1)` Results

---

.center[

```{r log_renda}
load('../data/output_data/ibge_sp.RData')

load('../data/output_data/voronoi_t1_sp.RData')

data %<>%
  mutate(homens = homens/pop,
         mulheres = mulheres/pop,
         brancos = raca_branca/pop,
         ate_25 = ate_25/pop,
         de_25_ate_40 = de_25_ate_40/pop,
         de40_ate_55 = de40_ate_55/pop,
         maior_55 = maior_55/pop,
         analf = (1 - analfabetos/pop)) %>% 
  rename('dens_dom' = 'dens_domiciliar',
         'renda' = 'renda_media',
         'de25_ate_40' = 'de_25_ate_40') %>% 
  select(cod_setor, renda, dens_dom, pop, analf, 
         brancos, homens, ate_25, de25_ate_40,
         de40_ate_55, maior_55)

data_aux <- data %>% 
  mutate(information = 'Census') %>% 
  rename('ID' = 'cod_setor') %>% 
  select(ID, information, renda)

vor_aux <- voronoi_t1 %>% 
  mutate(information = 'Voronois') %>% 
  select(ID, information, renda)

data_aux <- rbind(data_aux, vor_aux)

rm(vor_aux)

ggplot(data_aux) +
  geom_sf(aes(fill = log(renda)), size = 0, color = 'transparent') +
  scale_fill_gradient2(low = 'red', mid = 'white', 
                        high = 'blue',
                        midpoint = median(log(data_aux$renda), na.rm = T), 
                        guide = guide_colorbar(ticks = F, 
                                               title = 'Avg. Income')) +
  facet_wrap(~information) +
  theme_bw() +
  theme(strip.background = element_rect(fill = 'black', colour = 'white'),
        axis.text = element_blank(), 
        strip.text = element_text(color = 'white'),
        panel.background = element_rect(fill = 'black', color = 'white')) +
  ylab('log(Income)')

rm(data_aux)
```

]

</br>

.footnote[Our method used `r scales::percent(sum(voronoi_t1$pop)/sum(data$pop))` 
of the total population.]

---

.center[

```{r correlation}
ggplot(voronoi_t1) +
  geom_point(aes(x = PSDB, y = log(renda)), alpha = .2, shape = 19) +
  geom_smooth(aes(x = PSDB, y = log(renda)), method = 'lm') + 
  theme_bw() +
  theme(strip.background = element_rect(fill = 'transparent')) +
  xlab('% votes - PSDB') +
  ylab('log(Income)')
```

]

</br>

.footnote[Correlation: `r formatC(cor(log(voronoi_t1$renda), voronoi_t1$PSDB, use = 'complete.obs'))`.]

---

class: middle

.pull-left[

```{r pca}
voronoi_test <- voronoi_t1 %>% 
  as.data.frame() %>% 
  select(ID,PCB:`BRANCOS/NULOS`) %>% 
  # mutate_at(.vars = vars(starts_with('P|B')), .funs = funs(winner = colnames(.)[apply(.,1,which.max) %>% unlist]))
  # mutate(maior_votacao = get_party(.[grep('PCB|PCO', names(.))]))
  tidyr::gather('partido', 'votos', -ID) %>%
  group_by(ID) %>%
  # filter(votos == max(votos))
  arrange(-ID, -votos) %>%
  group_by(ID) %>%
  summarise(partido = first(partido)) %>% 
  select(ID, partido)

voronoi_t_2 <- voronoi_t1 %>% left_join(voronoi_test, by = 'ID')

rm(voronoi_test)

voronoi_t_2 %>% 
  as.data.frame() %>%
  mutate(renda = as.numeric(scale(renda)),
         dens_dom = as.numeric(scale(dens_dom))) %>% 
  select(renda:maior_55) %>%
  select(-pop) %>% 
  prcomp() -> pca

df <- data.frame(pc1 = pca$x[,1], pc2 = pca$x[,2],
                 pc3 = pca$x[,3], partido = voronoi_t_2$partido)

labs_pca <- scales::percent(pca$sdev/sum(pca$sdev))

(p1 <- ggplot(df) +
  geom_point(aes(x = pc1, y = pc2, color = partido), 
             shape = 19, alpha = .7, size = 2) +
  theme_bw() +
  xlab(paste0('PC1', ' ', '(', labs_pca[1], ')')) +
  ylab(paste0('PC2', ' ', '(', labs_pca[2], ')')) +
  guides(color = F) +
  theme(strip.background = element_rect(fill = 'transparent')))

# p2 <- ggplot(df) +
#   geom_point(aes(x = pc1, y = pc3, color = partido), 
#              shape = 19, alpha = .7, size = 2) +
#   theme_bw() +
#   xlab(paste0('PC1', ' ', '(', labs_pca[1], ')')) +
#   ylab(paste0('PC3', ' ', '(', labs_pca[3], ')')) +
#   guides(color = guide_legend(title = NULL)) +
#   theme(legend.position = 'top', legend.direction = 'horizontal')

# legends <- cowplot::get_legend(p2)

p2 <- ggplot(df) +
  geom_point(aes(x = pc1, y = pc3, color = partido), 
             shape = 19, alpha = .7, size = 2) +
  theme_bw() +
  xlab(paste0('PC1', ' ', '(', labs_pca[1], ')')) +
  ylab(paste0('PC3', ' ', '(', labs_pca[3], ')')) +
  guides(color = F) +
  theme(strip.background = element_rect(fill = 'transparent'))

# cowplot::plot_grid(p1, p2, ncol = 2, align = 'hv')

# rm(list = ls()[ls() != 'voronoi_t1'])
```

]

.pull-right[

```{r pca_2}

p2

rm(list = ls()[ls() != 'voronoi_t1'])

```


]

---

.center[

```{r final_plot}
p1 <- ggplot(voronoi_t1) +
  geom_sf(aes(fill = PT), size = 0, color = 'transparent') +
  scale_fill_gradient2(low = 'red', mid = 'white', 
                       high = 'blue',
                       midpoint = median(voronoi_t1$PT, na.rm = T), 
                       limits = c(min(voronoi_t1$PT, na.rm = T), 
                                  max(voronoi_t1$PT, na.rm = T))) +
  theme_bw() +
  theme(strip.background = element_rect(fill = 'transparent'),
        axis.text = element_blank()) +
  guides(fill = F) +
  ggtitle('% PT')

p2 <- ggplot(voronoi_t1) +
  geom_sf(aes(fill = PSB), size = 0, color = 'transparent') +
  scale_fill_gradient2(low = 'red', mid = 'white', 
                       high = 'blue',
                       midpoint = median(voronoi_t1$PSB, na.rm = T), 
                       limits = c(min(voronoi_t1$PSB, na.rm = T), 
                                  max(voronoi_t1$PSB, na.rm = T))) +
  theme_bw() +
  theme(strip.background = element_rect(fill = 'transparent'),
        axis.text = element_blank()) +
  guides(fill = F) +
  ggtitle('% PSB')

p3 <- ggplot(voronoi_t1) +
  geom_sf(aes(fill = PSDB), size = 0, color = 'transparent') +
  scale_fill_gradient2(low = 'red', mid = 'white', 
                       high = 'blue',
                       midpoint = median(voronoi_t1$PSDB, na.rm = T), 
                       limits = c(min(voronoi_t1$PSDB, na.rm = T), 
                                  max(voronoi_t1$PSDB, na.rm = T))) +
  theme_bw() +
  theme(strip.background = element_rect(fill = 'transparent'),
        axis.text = element_blank()) +
  guides(fill = F) +
  ggtitle('% PSDB')


p4 <- ggplot(voronoi_t1) +
  geom_sf(aes(fill = log(renda)), size = 0, color = 'transparent') +
  scale_fill_gradient2(low = 'red', mid = 'white', 
                       high = 'blue',
                       midpoint = log(2*510)) +
  theme_bw() +
  theme(strip.background = element_rect(fill = 'transparent'),
        axis.text = element_blank()) +
  guides(fill = F) +
  ggtitle('log(Income)')

p5 <- ggplot(voronoi_t1) +
  geom_sf(aes(fill = brancos), size = 0, color = 'transparent') +
  scale_fill_gradient2(low = 'red', mid = 'white', 
                       high = 'blue',
                       midpoint = .5, limits = c(0, 1)) +
  theme_bw() +
  theme(strip.background = element_rect(fill = 'transparent'),
        axis.text = element_blank()) +
  guides(fill = F) +
  ggtitle('% white people')

p6 <- ggplot(voronoi_t1) +
  geom_sf(aes(fill = analf), size = 0, color = 'transparent') +
  scale_fill_gradient2(low = 'red', mid = 'white', 
                       high = 'blue',
                       midpoint = median(voronoi_t1$analf)) +
  theme_bw() +
  theme(strip.background = element_rect(fill = 'transparent'),
        axis.text = element_blank()) +
  guides(fill = F) +
  ggtitle('Illiteracy rate')

cowplot::plot_grid(p1, p2, p3, p4, p5, p6, ncol = 3, 
                   align = 'hv')
```

]

---

# Other applications

.middle[

- Verifying the socio-economic profile of the population living in the neighborhood of UBS (basic health units)
- Given a clients data base with addresses, you can know about the social profile of them using our method

]

---